\Large Co-evolution of lexical meaning \& pragmatic use\\ {\bf Revision Cover letter}

### 2018-03-28 paper/rv-letter1.tex
cover lett answer

\begin{itemize}
\item We have tried to improve the exposition of the model, both on the technical side and on
  the way the model can be interpreted (re reviewer 1's concerns about how to interpret
  particular formulas and the model as a whole). There are now three very short appendix
  chapters, each with formal detail about how to better understand the abstract model. There is
  also the new section~2.3 dedicated to an explicit discussion of how to interpret the replicator
  mutator dynamic and a formal derivation of one particular agent-level update process which
  gives rise to this dynamic at the population level (appendix B).
\item Where previously we only had one simulation-based case study, we now complement these
  results with a more in-depth case study, presented in the new section 3.1, which focuses on a
  subset of types present in the larger case study presented in sections 3.2 and 3.3. This
  helps tie in our results closer to known results from the literature (re reviewer 2's comment
  2) and also helps understand the inner workings of the model better for the case at hand. It
  also makes clearer in which sense we may speak of ``co-evolution of semantics and
  pragmatics'' (in response to reviewer 1's comment).
\item To compensate for the added material, we also tried to shorten the paper. We tried to
  avoid repetitive formulations, delegated more detailed explanations to footnotes and omitted
  certain passages that we feel are interesting, but are possibly also too distracting in a
  paper that is already quite long and also partly rather technical.
\end{itemize}

@@

As we discuss in Section~1, our case study focuses on scalar implicatures because they are
well-studied systematic pragmatic inferences that have received much attention, both
theoretically and experimentally. This makes them suitable candidates for the study of the
evolution of regular pragmatic inferences; past research can guide our modeling choices and aid
in evaluating our application to the study of these inferences. This ties in with our
particular choices to model the pragmatic use of scalar expressions. As we now make more
explicit in \S 2.3.1, these draw from a growing game-theoretic and Bayesian tradition
\citep[e.g.,][]{franke:2009,FrankeJager2015:Probabilistic-p,GoodmanFrank2016:Pragmatic-Langu}.

@@

\stepcounter{reviewerCommentCounter} %increase counter
\noindent Reviewer \thereviewerCounter~asks for a clearer description of the model. As noted
earlier, we have taken care to make the exposition more accessible and to guide the reader more
through the technical details of Section 2. In particular, the newly added sections 2.3, 3.1,
and the appendix sections should help readers unravel the model and understand its conceptual
interpretation and inner mechanisms much better than before. We used the following questions
from Reviewer 1, briefly answered below, to guide the changes made in this new version.

@@

\vspace{.5cm}
\begin{mdframed}[backgroundcolor=gray!25,linecolor=gray!25]
How exactly are pragmatic strategies inherited/inferred by learners?    I think all of this may be in the formulas, but it would be useful if it was expressed in prose too.
\end{mdframed}
In short, a type is a combination of a lexicon and a disposition to act on it. Together, both ingredients define an agent's linguistic behavior. A learner faced with input $d$ (see above) calculates $P(\tau \mid d)$, the probability that a type $\tau$ produced input $d$. Crucially, neither linguistic strategies nor lexical meanings are directly observable, so they can only be faithfully recovered inasmuch as the {\em overt} behavior evidenced by a type -- the data it produces -- is (in tendency) attributable to only one, {\em covert}, pairing of a lexicon and a linguistic strategy.

@@

We have thoroughly revised the manuscript to make the contrast between these three predictions clearer (see Section~3.3, particularly 3.3.3; but also Section~3.1, which illustrates how the dynamics behave in a smaller type space; as well as the discussion of iterated learning alone and its dependence on $\lambda$ and $l$ in Sections 2.4.3 and appendix C). These questions tie in with Reviewer $1$'s request for a clearer exposition and the explanation of why we speak of co-evolution in this case (reviewer 1, comment 1). In a nutshell, pressure for learnability alone does not put the types in a population in competition. Instead, the population comes to be inhabited by types that are recovered from learning input of replicated types more often -- of which there might be many (e.g., all variants of a kind are equally learnable; if there are many variants of a type that is, in tendency, acquired more often, then the population will stay polymorphic). What fitness-relative selection adds to this process is the competition that learnability alone lacks, independent of the type space we look at. Now, in the case of our type space we have a slight (modulo $\lambda$) communicative disadvantage for targets relative to competitors, for instance. However, the fact that targets are inferred more often by na\"ive learners (by asymmetries in production likelihoods, see appendix C; a tendency which is also mediated by $\lambda$ and $l$), leads (i) to the gradual existence of less competitors, counteracting this functional disadvantage, as well as (ii) to the existence of only one variant of a kind (contra what we get in the {\em learning alone} condition).
%

@@

More concretely, there is a technical reason why we would like all speaker types to produce any message with positive probability: we do not want to make types too easily identifiable by even small sets of observed data, so that iterated learning has some work to do. Moreover, we belief that while a logarithmic definition of speaker utilities is just fine, when it comes to evolutionary fitness, a definition in terms of beliefs is not. Fitness should track genuine observable interaction with the world. Just holding a ``good belief'' gives no countable or observable advantage unless it is acted upon in some manner.

>>>>

\begin{itemize}
\item We improved the exposition of the model, both on the technical side and on
  the way the model can be interpreted (re reviewer 1's concerns about how to interpret
  particular formulas and the model as a whole). There are now three very short appendix
  chapters, each with formal detail about how to better understand the abstract model. There is
  also the new section~2.3 dedicated to an explicit discussion of how to interpret the replicator
  mutator dynamic and a formal derivation of one particular agent-level update process which
  gives rise to this dynamic at the population level (appendix B).
\item Where previously we only had one simulation-based case study, we now complement these
  results with a more in-depth case study, presented in the new section 3.1, which focuses on a
  subset of types present in the larger case study presented in sections 3.2 and 3.3. This
  helps tie in our results closer to known results from the literature (re reviewer 2's comment
  2) and also helps understand the inner workings of the model better for the case at hand. It
  also makes clearer in which sense we may speak of ``co-evolution of semantics and
  pragmatics'' (in response to reviewer 1's comment).
\item To compensate for the added material, we also shortened the paper. We tried to
  avoid repetitive formulations, delegated more detailed explanations to footnotes and omitted
  certain passages that we feel are interesting, but are possibly also too distracting in a
  paper that is already quite long and also partly rather technical.
\end{itemize}

@@

As we discuss in Section~1, our case study focuses on scalar implicatures because they are
well-studied systematic pragmatic inferences that have received much attention, both
theoretically and experimentally. This makes them suitable candidates for the study of the
evolution of regular pragmatic inferences because past research can guide our modeling choices and aid
in evaluating our application to the study of these inferences. This ties in with our
particular choices to model the pragmatic use of scalar expressions. As we now make more
explicit in \S 2.3.1, these draw from a growing game-theoretic and Bayesian tradition
\citep[e.g.,][]{franke:2009,FrankeJager2015:Probabilistic-p,GoodmanFrank2016:Pragmatic-Langu}.

@@

\stepcounter{reviewerCommentCounter} %increase counter
\noindent Reviewer \thereviewerCounter~asks for a clearer description of the model. As mentioned above, we have taken care to make the exposition more accessible and to guide the reader more
through the technical details of Section 2. In particular, the newly added sections 2.3, 3.1,
and the appendix sections should help readers unravel the model and understand its conceptual
interpretation and inner mechanisms much better than before. We used the following questions
from Reviewer 1, briefly answered below, to guide the changes made in this new version.

@@

\vspace{.5cm}
\begin{mdframed}[backgroundcolor=gray!25,linecolor=gray!25]
How exactly are pragmatic strategies inherited/inferred by learners?    I think all of this may be in the formulas, but it would be useful if it was expressed in prose too.
\end{mdframed}
In short, a type is a combination of a lexicon and a disposition to act on it. Together, both ingredients define an agent's linguistic behavior. A learner faced with input $d$ (see above) calculates $P(\tau \mid d)$, the probability that type $\tau$ produced input $d$. Crucially, neither linguistic strategies nor lexical meanings are directly observable, so they can only be faithfully recovered inasmuch as the {\em overt} behavior evidenced by a type -- the data it produces -- is (in tendency) attributable to only one, {\em covert}, pairing of a lexicon and a linguistic strategy.

@@

We have thoroughly revised the manuscript to make the contrast between these three predictions clearer (see Section~3.3, particularly 3.3.3; but also Section~3.1, which illustrates how the dynamics behave in a smaller type space; as well as the discussion of iterated learning alone and its dependence on $\lambda$ and $l$ in Sections 2.4.3 and appendix C). These questions tie in with Reviewer $1$'s request for a clearer exposition and the explanation of why we speak of co-evolution in this case (reviewer 1, comment 1). In a nutshell, pressure for learnability alone does not put the types in a population in competition. Instead, the population comes to be inhabited by types that are recovered from learning input of replicated types more often -- of which there might be many (e.g., all variants of a kind are equally learnable; if there are many variants of a type that is, in tendency, acquired more often, then the population will stay polymorphic). What fitness-relative selection adds to this process is the competition that learnability alone lacks, independent of the type space we look at. In the case of our type space we have a slight (modulo $\lambda$) communicative disadvantage for targets relative to competitors, for instance. However, the fact that targets are inferred more often by na\"ive learners (by asymmetries in production likelihoods, see appendix C; a tendency which is also mediated by $\lambda$ and $l$), leads (i) to the gradual existence of less competitors, counteracting this functional disadvantage, as well as (ii) to the existence of only one variant of a kind (contra what we get in the {\em learning alone} condition).
%

@@

More concretely, there is a technical reason why we would like all speaker types to produce any message with positive probability: we do not want to make types too easily identifiable by even small sets of observed data, so that iterated learning has some work to do. Moreover, we believe that while a logarithmic definition of speaker utilities is just fine, when it comes to evolutionary fitness, a definition in terms of beliefs is not. Fitness should track genuine observable interaction with the world. Just holding a ``good belief'' gives no countable or observable advantage unless it is acted upon in some manner.
